Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-10-14 Notes/model.tex
Added a theoretical (mis-)explanation for adding up covariance matrices.

\subsection{Soft occlusion regions}
Let the projections of hypothesized soft ellipsoids be
$\projectionOf{\dimsn{i}}$ with some mean $\mu_i$ and variance $\Sigma_i$
(assuming that projection of ellipsoids can be approximated by ellipses on
image plane). We take the occlusion (intersection of two ellipses) to be
modelled by product of the respective Gaussians.
%
\begin{align}
  O_{ij}(x; \mu_{Oij}, \Sigma_{Oij}) = N(x; \mu_i, \Sigma_i)N(x; \mu_j,
  \Sigma_j)
\end{align}
%
The product of Gaussian can be computed analytically.

\subsection{Merging occlusion regions with detection score}
But what does detection score function represents? It is a measure of
correlation of trained object features and the features in the candidate
bounding box. If the detection scores are indeed Gaussians around the mean
bounding box $\mu_j$, the $\Sigma_j^{-1}$ represents the variance (and
covariance) around the mean bounding box. But when the candidate objects seem
to be occluded we have additional information available. In such a case, we
can say that the occluded object might have unexpected effect on the detection
scores. However, the uncertainty in the detection score in loop sided. The
mean detection bounding box must have picked up correct boundaries on the
un-occluded sides but we cannot say the same about occluded boundaries. The
effect on detection score depends a lot on the features of the occluder. Given
this understanding we want to decrease our confidence on the mean detection
boundaries around the occluded boundaries. One of the simplest ways will be to
scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
factor.

@@

With our
discussion so far, the function $O_{ij}(.)$ gives an additional measure of
uncertainty associated with each point in the space. To finally re-model our
detection scores scaled by continuous occlusion we sample $O_{ij}(.)$ at the
mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
variance by $\mathcal{P}_{ij} = \rho_{ij}\rho_{ij}^\top$ where $\rho_{ij} =
\mathbf{1} + O_{ij}(\mu^{(d)}_j; \mu'_{Oij}, \Sigma'_{Oij})$. The new variance
in detection score is given by 
%
\begin{align}
  \Sigma'^{(d)}_j = \prod_{k \in \text{occluders}} \mathcal{P}_{kj}
  \Sigma^{(d)}_j
  \prod_{k \in \text{occluders}} \mathcal{P}^\top_{kj}
\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
\begin{align}
  S'(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}

>>>>

\subsection{Soft occlusion regions}
The soft occlusion regions is exactly the $\Ptrans$
%
\begin{align}
  O_{j}(x; \mu_{Oj}, \Sigma_{Oj}) = 1 - \Ptrans
\end{align}
%

\subsection{Merging occlusion regions with detection score}
What does detection score function represents? It is a measure of
correlation of trained object features and the features in the candidate
bounding box. If the detection scores are indeed Gaussians around the mean
bounding box $\mu_j$, the $\Sigma_j^{-1}$ represents the variance (and
covariance) around the mean bounding box. But when the candidate objects seem
to be occluded we have additional information available. In such a case, we
can say that the occluded object might have unexpected effect on the detection
scores. However, the uncertainty in the detection score in loop sided. The
mean detection bounding box must have picked up correct boundaries on the
un-occluded sides but we cannot say the same about occluded boundaries. The
effect on detection score depends a lot on the features of the occluder. Given
this understanding we want to decrease our confidence on the mean detection
boundaries around the occluded boundaries. One of the simplest ways will be to
scale the appropriate diagonal element of $\Sigma_j$ by an appropriate scaling
factor. But how does occlusion affects the non diagonal terms. Consider that we
have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
affect of uncertainty on mean and variance of existing observations. On adding
noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
\Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
\begin{multline}
  E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
  + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
\end{multline}
where the terms $E(x \Delta x^\top)$ denote the correlation between the data
vector and the uncertainty in the data. Although we understand that in our case
the data is the appearance based detection score and uncertainty because of
occlusion is closely related to the appearance and hence detection score, we
assume independence between $x$ and $\Delta x$. Hence our resultant covariance
matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$

@@

With our
discussion so far, the function $O_{ij}(.)$ gives an additional measure of
uncertainty associated with each point in the space. To finally re-model our
detection scores scaled by continuous occlusion we sample $O_{ij}(.)$ at the
mean detection boundaries from GMM $S(.)$ and we scale the detection boundary
variance by $\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} =
O_{j}(\mu^{(d)}_i; \mu'_{Oj}, \Sigma'_{Oj})$. The new variance
in detection score is given by 
%
\begin{align}
  \Sigma'^{(d)}_j = \mathcal{P}_{j}
  + \Sigma^{(d)}_j
\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
\begin{align}
  S'(\bb{i}) = \sum_j A_j \exp((\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}
